\sout{Machine Learning for Global Conquest} \\ Multimatrices and Their Derivatives

### 2020-08-08 Math/book.tex
Flushing out integration for multimatricies

TODO: cheeky quote

\begin{definition}[Multimatrix Wildcard Notation]
TODO: rigorous definition

Example:
$\shape{X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]} = \vec{s}$
\end{definition}

@@

\begin{quote}
TODO: cheeky quote
\end{quote}

@@

But what does this actually mean? I'll show, below, that this actually breaks down into
a series of line integrals from over a strait line from $A$ to $B$. It will also be
shown that the integral of $dF/dX$ will return $F(X) + C$, as one would expect from an
integral.

\begin{theorem}[Line Integrals Inside Multimatrix Integral]
If $G(X)$ is an integrable multimatrix function (i.e. it has a shape
$\shape{G(X)} = \vec{g} \oplus \shape{X}$) then each output element of it's
integral is a line integral.
Specifically, for all $\bar{g}$ in $\Dim(\vec{g})$,
\[ \left(\int_A^B G(X) dX\right)[\bar{g}] = \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
Where $C$ is the straight line from $A$ to $B$. And $\mmult{\shape{\shape{X}}} dX$ serves the same notational purpose as
$\cdot dr$ (see \cite{wiki:line_int}) because multiplication by the entire shape of $X$ is the same as a dot product.
\end{theorem}
\begin{proof}
Let us parameterize $C$ such that $C(t) = A + t(B-A)$. Then $dC/dt = B-A$ and
we can rewrite the line integral over $C$ as,
\[ \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX = \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt \]
TODO
\end{proof}

TODO:fundamental theorem

>>>>

\begin{displayquote}
\textbf{Julian Bashir:} They broke seven of your transverse ribs and fractured your clavicle.

\textbf{Elim Garak:} Ah, but I got off several cutting remarks, which no doubt did serious damage to their egos.

(Star Trek Deep Space Nine, Season 4. Episode 1 \& 2 \cite{stds9})
\end{displayquote}

\begin{definition}[Multimatrix Wildcard Notation]
Example:
$\shape{X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]} = \vec{s}$
\end{definition}

\begin{theorem}[Wildcard Multiplication]
TODO:generalize
Let $A$ and $X$ be multimatrixes of shape $\shape{A} = \vec{a} \oplus \vec{x}$ and $\shape{X} = \vec{x}$ respectively.
Then $A[\bar{a} \oplus *^{\vec{x}}] \mmult{\shape{\vec{x}}} X = (A \mmult{\shape{\vec{x}}} X)[\bar{a}]$.
\end{theorem}
\begin{proof}
\begin{align*}
  A[\bar{a} \oplus *^{\vec{x}}] \mmult{\shape{\vec{x}}} X
  &=
  \sum_{\forall \bar{x} \in \Dim(\vec{X})} A[\bar{a} \oplus *^{\vec{x}}][\bar{x}] X[\bar{x}] \\
  &=
  \sum_{\forall \bar{x} \in \Dim(\vec{X})} A[\bar{a} \oplus \bar{x}] X[\bar{x}] \\
  &= (A \mmult{\shape{\vec{x}}} X)[\bar{a}]
\end{align*}
\end{proof}

@@

\begin{displayquote}
TODO: cheeky quote
\end{displayquote}

@@

\begin{landscape}
But what does this actually mean? I'll show, below, that this actually breaks down into
a series of line integrals from over a strait line from $A$ to $B$. It will also be
shown that the integral of $dF/dX$ will return $F(X) + C$, as one would expect from an
integral.

\begin{theorem}[Line Integrals Inside Multimatrix Integral]
\label{line_inside}
If $G(X)$ is an integrable multimatrix function (i.e. it has a shape
$\shape{G(X)} = \vec{g} \oplus \shape{X}$) then each output element of it's
integral is a line integral.
Specifically, for all $\bar{g}$ in $\Dim(\vec{g})$,
\[ \left(\int_A^B G(X) dX\right)[\bar{g}] = \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
Where $C$ is the straight line from $A$ to $B$. And $\mmult{\shape{\shape{X}}} dX$ serves the same notational purpose as
$\cdot dr$ (see \cite{wiki:line_int}) because multiplication by the entire shape of $X$ is the same as a dot product.
\end{theorem}
\begin{proof}
Let us parameterize $C$ such that $C(t) = A + t(B-A)$. Then $dC/dt = B-A$ and
we can rewrite the line integral over $C$ as,
\[ \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX = \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt \]
For which we can write out the Riemann integral \cite{wiki:riemann_int}:
\begin{align*}
  \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt
  &=
  \lim_{n \to \inf} \sum_{i=1}^n G(C(i/n))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt}(i/n) \frac{1}{n} \\
  &=
  \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{B-A}{n} \\
  &=
  \lim_{n \to \inf} \sum_{i=1}^n \left( G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
  &=
  \left( \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
  &=
  \left(\int_A^B G(X) dX\right)[\bar{g}] 
\end{align*}
\end{proof}
\end{landscape}

This leads us to my final observation about integrals.

\begin{theorem}[Integral of Multimatrix Derivatives]
For any multimatrix function $F(X)$,
\[ \int_A^B \frac{dF}{dX} dX = F(B) - F(A) \]
\end{theorem}
\begin{proof}
We know from the above theorem \ref{line_inside} that for all $\bar{f} \in \Dim(\vec{f})$
\[ \left(\int_A^B \frac{dF}{dX}(X) dX\right)[\bar{f}] = \int_C \frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
Notice that $\frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}]$ is the equivalent
to the gradient of $F(X)[\bar{f}]$ at $X$ since for all $\bar{x} \in \Dim(\vec{x})$,
\[ \frac{dF}{dX}(X)[\bar{f} \oplus \bar{x}] = \frac{\partial F[\bar{f}]}{\partial X[\bar{x}]} \]
Then by the Gradient theorem \cite{wiki:gradient_thm} we can conclude that,
\[ \left(\int_A^B \frac{dF}{dX}(X) dX\right)[\bar{f}] =  F(B)[\bar{f}] - F(A)[\bar{f}] = \left( F(B)-F(A) \right)[\bar{f}] \]
So, 
\[ \int_A^B \frac{dF}{dX} dX = F(B) - F(A) \]
\end{proof}
